\documentclass{article}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{bbold}
\usepackage[colorlinks=true,urlcolor=blue]{hyperref}
\usepackage[a4paper, total={7in,10in}]{geometry}

\begin{document}
\section{What is a Proof?}
\subsection{Problem 1.1}
Can't easily do a visual prolem in \LaTeX, and I am too lazy to create graphics for this. I will try to use my words instead.
\subsubsection{Problem 1.1 (a)}
Arrange the triangles so that the ``a'' side of one is on the ``b'' side of the other, with the acute angles touching. Do this for all of them, and the ``c'' sides will form an outer square of size $c\times c$, and the square hole in the middle will be of size $(b-a)\times(b-a)$.
\subsubsection{Problem 1.1 (b)}
Move two adjacent triangles to the opposite side of the $c\times c$ sqaure, so that their ``c'' sides are flush, forming two $a\times b$ rectangles, touching each other and the $(b-a)\times(b-a)$ square. This forms a single shape (that looks like a 'P' turned $90^{\circ}$ to the right. They form two squares of size $a\times a$ and $b\times b$. The $b\times b$ square includes the $(b-a)\times(b-a)$ square, one of the $b\times a$ rectangles, and a small section of the other one. The $a\times a$ square is formed with the rest of that rectangle.
\subsubsection{Problem 1.1 (c)}
In the case of $a=b$, The $(b-a)\times(b-a)$ rectangle becomes a degenerate $0\times0$ rectangle. However this does not pose a problem the proof still holds. As $a=b$, the triangles are right-angle isoceles triangles. For (a), the triangles form a square with the sides forming an ``$\times$'' in the middle. For part (b), the triangles are rearranged into a $a\times2a$ rectangle, made up of two $a\times a$ squares, which shows that $a^2 + a^2 = a^2 + b^2 = c^2$ using the preservation of area under rearrangement.
\subsubsection{Problem 1.1 (d)}
1. That the two acute angles of a right-angled triangle sum to $90^{\circ}$.\\
2. When putting the right angle of a right-angled triangle against a straight line, they form a retroflex right angle (For part (a), these become the corners of the square).\\
3. That if you put a line of length $a$ along a line of length $b$, the remaining length not covered by the first line is of length $b-a$.\\
4. That is a shape has 4 right-angles and equal sides, it is a square. (I am not as confident in this one, because, isn't this the defintion of a square??)\\
5. That the acute angles from two right-angle triangles together sum to $180^{\circ}$.
\subsection{Problem 1.2}
\subsubsection{Problem 1.2 (a)}
$\sqrt{(-1)(-1)}=\sqrt{-1}\sqrt{-1}$ is not true.
\subsubsection{Problem 1.2 (b)}
Assume $1=-1$.
\begin{align}
  1 &= -1 \\
  \implies 2 &= 0 \\
  \implies 1 &= 0 \\
  \implies 2 &= 1
\end{align}
\subsubsection{Problem 1.2 (c)}
$$\sqrt{rs} = (rs)^{\frac{1}{2}} = r^{\frac{1}{2}}s^{\frac{1}{2}} = \sqrt{r}\sqrt{s}$$
\subsection{Problem 1.3}
\subsubsection{Problem 1.3 (a)}
$\log_{10}{(1/2)}$ is negative, and thus you cannot multiply both sides of the inequality without flipping the ``$>$'' into a ``$<$''.
\subsubsection{Problem 1.3 (b)}
``$\$$'' and ``¢'' should be treated as units. As $\$1=\$=100\text{¢}$, the first step is valid. However, the step $\$0.01 = (\$0.1)^2$ is invalid because the RHS expands to $\$^20.01$, which is not equal to $\$0.01$ as $\$^2\ne\$$. Similarly, the step $(10\text{¢})^2 = 100\text{¢}$ is invalid.
\subsubsection{Problem 1.3 (c)}
When $a=b$, $a-b$ is equal to $0$, thus cancelling the $(a-b)$'s is invalid as it is dividing by zero.
\subsection{Problem 1.4}
While the implications going from each statement each happen to be true, this is not a valid proof as the directionality of the implicaitons should be reversed. If the proof started with $(a-b)^2 \ge 0$ and did the steps in reverse, finishing at $\frac{a+b}{2} \ge \sqrt{ab}$, then the proof would have been valid.
\subsection{Problem 1.5}
This is the \href{https://en.wikipedia.org/wiki/Unexpected_hanging_paradox}{Unexpected Hanging Paradox}, and there is no consensus to its nature. My opinion is that the ``it will be a surprise'' element of the statement is equivalent to ``the day cannot be deduced from this statement''. But, this is self-referencial, leading to a paradox in a manner similar to the \href{https://en.wikipedia.org/wiki/Liar_paradox}{Liar Paradox}.
\subsection{Problem 1.6}
We use proof by contradiction.\\
Suppose ``$log_7n$ is either an integer or irrational'' is false. This is equivalent to ``$log_7n$ is a rational number and not an integer''.
\begin{align}
  log_7n &= \frac{p}{q}\text{ where coprime }p,q\in\mathbb{Z}^+ && \text{definition of rational number} \\
  qlog_7n &= p && \text{multiply both sides by }q\text{ as }q\in\mathbb{Z}^+\implies q\ne0 \\
  log_7n^q &= p && ylog_bx=log_bx^y \\
  7^{log_7n^q} &= 7^p \\
  n^q &= 7^p && b^{log_bx} = x
\end{align}
Note that the prime-factorisation of the RHS must be equal to the prime-factorisation of the RHS. Thus $n^q$ is made up entirely of $7$'s. As exponentiation by $q$ does not change which primes are included in the factorisation, $n$ must thus be entirely made of $7$'s as well, i.e, $n$ is a power of $7$. Thus, $n=7^m$, where $m\in\mathbb{N}$. Thus, $n^q=(7^m)^q=7^{mq}=7^p$, since $(a^b)^c=a^{(bc)}$. Thus $mq=p$, since $x^a=x^b\implies a=b$.\\
\\
Note that either $m=0$, or $q$ is a factor of $p$ (since $mq=p$ and $m,q,p\in\mathbb{Z}^+$). If $q$ is a factor of $p$, then it is either $1$, $p$, or a non-trivial factor of $p$ (i.e., a factor that isn't $1$ or $p$).\\
\\
All of these cases lead to contradictions. If $m=0$, then $mq=0q=0=p$, since $0x=0$. But $p=0$ contradicts $p\in\mathbb{Z}^+$. If $q=1$, then $log_7n=\frac{p}{q}=\frac{p}{1}=p$, but this contradicts $log_7n$ being not an integer, as $p$ is an integer. If $q=p$, then $log_7n=\frac{p}{q}=\frac{p}{p}=1$, which is a contradiction with $log_7n$ not being an integer as $1$ is an integer. If $q$ is a non-trivial factor of $p$, then this contradicts $q$ and $p$ being coprime, as $p$ and $q$ share a common factor, namely $q$.\\
\\
Thus $log_7n$ is either an integer or irrational.
\hfill$\blacksquare$
\subsection{Problem 1.7}
\textbf{Case 1}: $r<s$\\
Since $r<s$, $max(r,s)=s$, and $min(r,s)=r$. Thus, $max(r,s)+min(r,s)=s+r=r+s$.\\
\\
\textbf{Case 2}: $r>s$\\
Since $r>s$, $max(r,s)=r$, and $min(r,s)=s$. Thus $max(r,s)+min(r,s)=r+s$.\\
\\
\textbf{Case 3}: $r=s$\\
Since $r=s$, $max(r,s)=max(r,r)=r$, and $min(r,s)=min(s,s)=s$. Thus $max(r,s)+min(r,s)=r+s$.\\
\\
Thus $max(r,s)+min(r,s)=r+s$ for all real numbers $r$, $s$, as it is true in all cases.\hfill$\blacksquare$
\end{document}
